Laws for Creating Trust in the Blockchain Age

### 2017-09-18 tex/article.tex
Minor change in taxi experiment

To study differences in matching efficiency between a market with a central clearinghouse and a fully decentralized network, we varied the percentage of taxi drivers performing matchmaking and the broadcast range of messages.
The results are presented in Figure \ref{fig:matching_efficiency}, showing matching efficiency as the network becoming increasingly decentralized.
The horizontal axis denotes the percentage of taxi drivers performing matchmaking whereas the vertical axis represents the average distance between a matched driver and passenger.
The points on each line in Figure \ref{fig:matching_efficiency} correspond to a network where 10\%, 20\%, 30\% etc. of the taxi drivers are performing matchmaking, except for points near zero percentage on the horizontal axis: they resemble the situation where there is exactly one entity performing matchmaking, like an Uber server.

>>>>

To study differences in matching efficiency between a market with a central clearinghouse and a fully decentralized network, we varied the percentage of taxi drivers performing matchmaking and the broadcast range of messages.
The results are presented in Figure \ref{fig:matching_efficiency}, showing matching efficiency as the network becoming increasingly decentralized.
The horizontal axis denotes the percentage of taxi drivers performing matchmaking whereas the vertical axis represents the average distance between a matched driver and passenger.
The points on each line in Figure \ref{fig:matching_efficiency} correspond to a network where 10\%, 20\%, 30\% etc. of the taxi drivers are performing matchmaking.
The only exception are the points near zero percentage on the horizontal axis: they resemble the situation where out of 550 taxis, exactly one taxi conducts all matchmaking activities, like an Uber server (thus 0.18\%).
